Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-23 doc/asplos13/tasks.tex

Third, the programmer can invoke a parallel for loop, provided that
the trip count is known at loop entry. The programmer
specifies a function pointer along with start and end indices and an
optional threshold to control parallel overhead. Grappa does {\em
recursive decomposition} of iterations, similar to Cilk's cilk\_for
construct~\cite {cilkforimplementation} \comment{could only find slides
page6 of
http://www.clear.rice.edu/comp422/lecture-notes/comp422-2012-Lecture5-
Cilk++.pdf    ---- Good enough.  Cite it.  -Mark} and TBB's {\tt parallel\_for}~\cite{intel_tbb}.  It generates a
logarithmically-deep tree of tasks, stopping to execute the loop body
when the number of iterations is below the required threshold.

>>>>

Third, the programmer can invoke a parallel for loop, provided that
the trip count is known at loop entry. The programmer
specifies a function pointer along with start and end indices and an
optional threshold to control parallel overhead. Grappa does {\em
recursive decomposition} of iterations, similar to Cilk's cilk\_for
construct~\cite {cilkforimplementation}.\comment{could only find slides
page6 of
http://www.clear.rice.edu/comp422/lecture-notes/comp422-2012-Lecture5-
Cilk++.pdf    ---- Good enough.  Cite it.  -Mark} and TBB's {\tt parallel\_for}~\cite{intel_tbb}.  It generates a
logarithmically-deep tree of tasks, stopping to execute the loop body
when the number of iterations is below the required threshold.
